Binning Strategies and Related Loss for Large Data

### 2015-02-26 Paper.Rnw
Notes about Pearson and Scott

>>>>

\ktm{I have read through the sections of Pearson (1895), Scott (1979) and Scott (1992) that pertained to binning. I will work on integrating them into the lit review next.  Scott talked much about the optimal choice of bin width based on MSE but there was not much talk about what to do with points at the boundaries of bins (he effectively assumed infinite precision in the measurement process to avoid it).

I will need to search more to find papers about the binning algorithms and the boundaries they set.  The \texttt{cut} function allows for intervals that are closed on either the left or right and also allows the points on the outermost open bound to be included in the last bin.

The \texttt{cut2} function allows the same type of quantile binning as discussed in Scott (1992).}
